Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-01 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Minor changes
Defining framework

%Please help with this paragraph, is evidence needed?
% It's the tuning of the algorithm which is data driven, not the
% algorithm itself, right? - JJ
% And evidence for what? - jj
In evolutionary computation algorithms are data driven since it is important to keep data about the 
population of each generation, in order to generate the next or even change certain parameters
or analyze the evolutionary process. 
% Human Centered Importance
The framework models the context of interaction along with the population and
this knowledge is available to be an integral part of the evolutionary computation.
%This could be generalized?
For example, in a C-IEC application, fitness assignment depend on the
actions of a social network of users. 
A stream of actions is triggered when they tag, share, rate, store or even delete a phenotype. The selection of parents could
also depend also on the previous actions, leveraging information such as the fact that they have the same tag, or are shared by
similar users. That knowledge could also be applied in choosing which phenotypes present to a certain
users, in order to give them those they will find more interesting or useful. 
% IoT
The context of interaction, can also include data retrieved from sensors and other IoT devices.
% Engagement
Data available from the interaction is also used to increase the performance of the system by applying 
gamification techniques. Gamification is defined by Deterding et al. as
``the use of game design elements in non-game contexts'' \cite{deterding2011game}.
The gamification element employed in a case study is a rewarding mechanism  
\cite{dubois2013understanding}, in general they consist of a reputation system with score points, 
levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level.

@@

\section{HC  IEC Framework}
  \subsection{Real World}
  \subsection{Data Model}
  \subsection{Evolutionary Algorithm}

>>>>

%Please help with this paragraph, is evidence needed?
% It's the tuning of the algorithm which is data driven, not the
% algorithm itself, right? - JJ
%  Tuning yes - Mario
% And evidence for what? - jj
%  That most EAs use only population data - Mario
In evolutionary computation algorithms are data driven since it is important to keep data about the 
population of each generation, in order to generate the next or even change certain parameters
or analyze the evolutionary process. 
% Human Centered Importance
The framework models the context of interaction along with the population and
this knowledge is available to be an integral part of the evolutionary computation.
%This could be generalized?
For example, in a C-IEC application, fitness assignment depend on the
actions of a social network of users. 
A stream of actions is triggered when they tag, share, rate, store or even delete a phenotype. 
The selection of parents could also depend also on the previous actions, leveraging information 
such as the fact that they have the same tag, or are shared by
similar users. That knowledge could also be applied in choosing which phenotypes present to a certain
users, in order to give them those they will find more interesting or useful. 
% IoT
The context of interaction, can also include data retrieved from sensors and other IoT devices.
% Engagement
Data available from the interaction is also used to increase the performance of the system by applying 
gamification techniques. Gamification is defined by Deterding et al. as
``the use of game design elements in non-game contexts'' \cite{deterding2011game}.
The gamification element employed in a case study is a rewarding mechanism  
\cite{dubois2013understanding}, in general they consist of a reputation system with score points, 
levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level.

@@

\section{HC  IEC Framework}
The general goal of this research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
The framework is a reusable architectural design together with an implementation \cite{campbell1991choices}. We deliberately use the more general term Human instead of User, because humans are not always playing the role of
users in software engineering sense, they could just be interacting 
naturally with their environment and with out knowing they are implicitly
evaluating a possible solution.

% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
% is a reusable design together with an implementation

The framework

in order to increase
participation and also to minimize the amount of evaluations needed for the
evolutionary process in a given IEC application.

  \subsection{Real World}
  \subsection{Data Model}
  \subsection{Evolutionary Algorithm}
